\documentclass{tutodoc}

\input{../../preamble.cfg.tex}


\begin{document}

\small

\begin{tdocbreak}
	\item Format: the \tdoccls{scrartcl} class replaces the venerable \tdoccls{article}. This implies better placement of the margin notes with the options retained for loading \tdoccls{scrartcl}.

	\item \LaTeX\ code: the macro \tdocmacro{tdocinlatex} has been renamed \tdocmacro{tdoclatexin}.

	\item Color key names will be hyphenated where necessary: this implies the following changes.
	%
	\begin{enumerate}
		\item Admonitions: the \tdoclatexin{colchges} option of the environments has been renamed \tdoclatexin{col-chges}.

		\item Showcases: for the environment \tdocenv*{tdocshowcase} and the macro \tdocmacro{tdocshowcaseinput}, the \tdoclatexin{colstripe} and  \tdoclatexin{coltext} options have been renamed \tdoclatexin{col-stripe} and \tdoclatexin{col-text}\,.
	\end{enumerate}
\end{tdocbreak}


\begin{tdocfix}
	\item Admonitions: for the \tdocmacro{newkeytheorem} used with the \tdoclatexin{draft} theme, \tdoclatexin{postheadhook = \leavevmode} has been added (this is necessary because the content can naturally be of the list type).
\end{tdocfix}


\begin{tdocnew}
	\item Documentation: addition of a section listing dependencies.

	\item Class options.
	%
	\begin{enumerate}
		\item Options not specific to \thisproj\ are passed on to the class in charge of general formatting.

		\item The \tdoccls{scrartcl} options \tdoclatexin{fontsize} and \tdoclatexin{DIV} can't be used because their values are fixed by \thisproj.
	\end{enumerate}

	\item The macro \tdocmacro{tdocinEN} respects the English linguistic rules.

	\item Admonitions.
	%
	\begin{enumerate}
		\item A new environment \tdocenv{tdoctodo} has been added.

		\item Each environment has a new option \tdoclatexin{col} for the color of the content indicating changes.
	\end{enumerate}
\end{tdocnew}


\begin{tdocupdate}
	\item \tdoclatexin{draft} theme and changes: the environments for the kind of changes stop to use icons.

	\item Documentation: the theme gallery uses a better fake example.
\end{tdocupdate}



\begin{tdoctech}
	\item Simplified organisation of configuration files in the final project.
	%
	\begin{enumerate}
		\item \texttt{CSS}-like: use of one file per theme with a name like \texttt{tutodoc-bw.css.cls}\,.

		\item Locale: use of names like \texttt{tutodoc-en.loc.cls}\,.
	\end{enumerate}
\end{tdoctech}

\end{document}
