\documentclass{tutodoc}

\input{../../preamble.cfg.tex}


\begin{document}

\small

\begin{tdocfix}
	\item Documentation: references to tools to indicate changes have been incorrectly written as characteristics of highlighted colored content.
\end{tdocfix}


\begin{tdocbreak}
	\item \LaTeX showcases: the default layout is more sober, and there are options for having just the rulers, or the colored stripe.

	\item Code formatting just in \LaTeX: the options system changes as shown next.
\end{tdocbreak}


\begin{tdocnew}
	\item Formatting of computer codes in addition to those specifically in LaTeX.
	%
	\begin{enumerate}
		\item Creation of \tdocenv{tdoccode} and \tdocmacro{tdoccodein}.

		\item For macros for inline code, and environments for blocks of code, \tdocpack{minted} options are indicated inside square brackets in the traditional way: \tdoclatexin{[minted options]}\,.

		\item For code block environments, \tdocpack{tcolorbox} options are indicated inside rafters: \tdoclatexin{<tcolorbox options>}\,.

		\item The new macro \tdocmacro{tdoctcb} allows you to use shortcuts for regularly used \tdocpack{tcolorbox} styles.
	\end{enumerate}

	\item Documentation: a new section presents tools for formatting computer codes other than those in LaTeX.
\end{tdocnew}


\begin{tdocupdate}
	\item Sub-sub-sections are numbered in lower case.

	\item Themes.
	%
	\begin{enumerate}
		\item Less space consumed.

		\item Shadows have better coloring.

		\item For all themes except the \tdoclatexin{draft} one, the radius of the arcs of the corners of the frames increases from \tdoclatexin{.75mm} to \tdoclatexin{.2pt},.

 		\item Codes just in \LaTeX: with the theme \tdoclatexin{color}, the background color changes from \tdoclatexin[bgcolor = yellow!4]{yellow!4} to \tdoclatexin{gray!5}.

		\item Changes: with the \tdoclatexin{dark} theme, the font of the \tdoclatexin{[Init]} text used by the \tdocmacro{tdocstartproj} macro is identical to that of the environment titles for typing changes.
	\end{enumerate}
\end{tdocupdate}

\end{document}
