\documentclass{tutodoc}

\input{../preamble.cfg.tex}


\begin{document}

\section{Indicate changes}
\label{tutodoc-changes}

To make it easier to monitor a project, it is essential to provide a history indicating the changes made when a new version is published.



\subsection{When?}
\label{tutodoc-changes-when}

You can either date something, or version it, in which case the version number can be dated.


% ------------------ %


\begin{tdocexa}[Dating new products]
    The \tdocmacro{tdocdate} macro is used to indicate a date in the margin, as in the following example.

    \tdoclatexshow{examples/version-n-change/dating.tex}
\end{tdocexa}


% ------------------ %


\begin{tdocexa}[Versioning new features, possibly with a date]
    Associating a version number with a new feature is done using the \tdocmacro{tdocversion} macro, with the colour and date being optional arguments.

    \tdoclatexshow{examples/version-n-change/versioning.tex}
\end{tdocexa}


\begin{tdocexa}[Caution with paragraph titles]
	The following example shows that a date and/or version must be placed just after a paragraph title, and not before it.

	\tdoclatexshow{examples/version-n-change/para-title.tex}
\end{tdocexa}


\begin{tdocexa}[Adjust vertical positioning]
	If required, you can modify the vertical offset used to place dates and versions in the margin, the default value being $(-8\,\mathit{pt})$.

	\tdoclatexshow{examples/version-n-change/manual-setting.tex}
\end{tdocexa}


\begin{tdocimp}
    \begin{enumerate}[wide]
        \item The \tdocmacro{tdocdate} and \tdocmacro{tdocversion} macros require two compilations.

        \item The final rendering of the dates takes into account the language detected by \thisproj{}: for example, if French is selected, the dates will be displayed in the format \texttt{DD/MM/YYYY}.
    \end{enumerate}
\end{tdocimp}


\begin{tdoccaut}
    Only the use of the digital format \tdoclatexin+YYYY-MM-DD+ is verified,%
    \footnote{
        Technically, checking the validity of a date using \LaTeX3 presents no difficulty.
    }
    and this is a choice! Why? Quite simply because dating and versioning explanations should be done semi-automatically to avoid any human bugs.
\end{tdoccaut}

\end{document}
