\documentclass[10pt, a4paper]{tutodoc}

\input{../preamble.cfg.tex}


\begin{document}

\subsection{Flashy content}
\label{tutodoc-admonitions}

\begin{tdocnote}
    Icons are obtained via the \tdocpack{fontawesome5} package, and text spacing is managed by the \tdocmacro{tdocicon} macro.
    \footnote{
        For example,
        \tdocinlatex|\fbox{\tdocicon{\faBed}{Tired}}|
        produces\,
        \fbox{\tdocicon{\faBed}{Tired}}\,.
    }
\end{tdocnote}


\subsubsection{A tip}

The \tdocenv*{tdoctip} environment is used to give tips. Here's how to use it.

\tdoclatexinput[sbs]{examples/admonitions/tip.tex}


\smallskip

\begin{tdocnote}
    Colors are obtained via the expandable macros \tdocmacro{tdocbackcolor} and \tdocmacro{tdocdarkcolor}.
    For further information, please refer to the end of the section \ref{tutodoc-color-macros} page \pageref{tutodoc-color-macros}.
\end{tdocnote}


\smallskip


\begin{tdoctip}
    Sometimes, highlighted content can be reduced to a list. In this case, the formatting can be improved as follows where we use the \tdocinlatex{wide} option from the \tdocpack{enumitem} package.
\end{tdoctip}

\tdoclatexinput[sbs]{examples/admonitions/leavevmode-items.tex}


\foreach \sectitle/\desc/\filename in {
    {Informative note}/%<-- Translate me!
    {The \tdocenv*{tdocnote} environment is used to highlight useful information. Here's how to use it.}/%<-- Translate me!
    note,
    %
    {Something important}/%<-- Translate me!
    {The \tdocenv*{tdocimp} environment is used to indicate something important but harmless.}/%<-- Translate me!
    important,
    %
    {Caution about a delicate point}/%<-- Translate me!
    {The \tdocenv*{tdoccaut} environment is used to indicate a delicate point to the user. Here's how to use it.}/% <-- Translate me!
    caution,
    %
    {Warning of danger}/%<-- Translate me!
    {The \tdocenv*{tdocwarn} environment is used to warn the user of a trap to avoid. Here's how to use it.}/%<-- Translate me!
    warn%
} {
    \subsubsection{\sectitle}

    \desc

    \tdoclatexinput[sbs]{examples/admonitions/\filename.tex}
}

\end{document}
