\documentclass[10pt, a4paper]{article}

\input{../preamble.cfg.tex}


\begin{document}

\subsection{Flashy content} \label{tdoc-colorful-highlight}

\begin{tdocnote}
    Icons are obtained via the \tdocpack{fontawesome5} package, and text spacing is managed by the \tdocmacro{tdocicon} macro.
    \footnote{
        For example,
        \tdocinlatex|\tdocicon{\faBed}{Tired}|
        produces\,
        \tdocicon{\faBed}{Tired}.
    }
\end{tdocnote}


\subsubsection{A tip}

The \tdocenv*{tdoctip} environment is used to give tips. Here's how to use it.

\tdoclatexinput[sbs]{examples/highlight/tip.tex}


\smallskip

\begin{tdocnote}
    Colors are obtained via the expandable macros \tdocmacro{tdocbackcolor} and \tdocmacro{tdocdarkcolor}.
    For further information, please refer to the end of the section \ref{tdoc-color-macros} page \pageref{tdoc-color-macros}.
\end{tdocnote}


\foreach \sectitle/\desc/\filename in {
	{Informative note}/%<-- Translate me!
	{The \tdocenv*{tdocnote} environment is used to highlight useful information. Here's how to use it.}/%<-- Translate me!
	note,
	%
	{Something important}/%<-- Translate me!
	{The \tdocenv*{tdocimp} environment is used to indicate something important but harmless.}/%<-- Translate me!
	important,
	%
	{Caution about a delicate point}/%<-- Translate me!
	{The \tdocenv*{tdoccaut} environment is used to indicate a delicate point to the user. Here's how to use it.}/% <-- Translate me!
	caution,
	%
	{Warning of danger}/%<-- Translate me!
	{The \tdocenv*{tdocwarn} environment is used to warn the user of a trap to avoid. Here's how to use it.}/%<-- Translate me!
	warn%
} {
	\subsubsection{\sectitle}

	\desc

	\tdoclatexinput[sbs]{examples/highlight/\filename.tex}
}

\end{document}
